Follow-up Samples

### 2017-09-13 submission/supplemental.Rmd
update abstract word count and supplemental to msphere

---
title: ""
bibliography:
csl: microbiome.csl
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
fontsize: 12pt
geometry: margin=1.0in
---

# Differences in the Stool Microbiome Before and After Colorectal Cancer Treatment

@@

adn_varsMDA <- read.csv('../data/process/tables/adn_reduced_model_top_vars_MDA_Summary.csv', header = T, stringsAsFactors = F)

srn_varsMDA <- read.csv('../data/process/tables/srn_reduced_model_top_vars_MDA_Summary.csv', header = T, stringsAsFactors = F)

crc_varsMDA <- read.csv('../data/process/tables/reduced_crc_model_top_vars_MDA_Summary.csv', header = T, stringsAsFactors = F)

# Create selection vector
common_vars <- common_vars_summary$otu
common_num <- as.numeric(gsub("Otu", "", common_vars_summary$otu))

# Create MDA vectors
adn_MDA <- filter(adn_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)
srn_MDA <- filter(srn_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)
crc_MDA <- filter(crc_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)

st2 <- select(common_vars_summary, otu) %>%
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$lowest_ID)) %>%
  mutate(otu = paste("OTU", common_num, sep = "")) %>%
  mutate(adn_MDA = round(adn_MDA$median_MDA, digits = 2), srn_MDA = round(srn_MDA$median_MDA, digits = 2), crc_MDA = round(crc_MDA$median_MDA, digits = 2)) %>%
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))

>>>>

---
title: ''
csl: microbiome.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: null
---

# Normalization of the microbiota in patients after treatment for colonic lesions

@@

adn_varsMDA <- read.csv('../data/process/tables/adn_MDA_Summary.csv', header = T, stringsAsFactors = F)

srn_varsMDA <- read.csv('../data/process/tables/srn_MDA_Summary.csv', header = T, stringsAsFactors = F)

crc_varsMDA <- read.csv('../data/process/tables/crc_MDA_Summary.csv', header = T, stringsAsFactors = F)

# Create selection vector
common_vars <- common_vars_summary$Variable
common_num <- as.numeric(gsub("Otu", "", common_vars_summary$Variable))

# Create MDA vectors
adn_MDA <- filter(adn_varsMDA, Variable %in% common_vars) %>% slice(match(common_vars, Variable)) %>% select(median_mda)
srn_MDA <- filter(srn_varsMDA, Variable %in% common_vars) %>% slice(match(common_vars, Variable)) %>% select(median_mda)
crc_MDA <- filter(crc_varsMDA, Variable %in% common_vars) %>% slice(match(common_vars, Variable)) %>% select(median_mda)

st2 <- select(common_vars_summary, Variable) %>%
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$tax_ID)) %>%
  mutate(otu = paste("OTU", common_num, sep = "")) %>%
  mutate(adn_MDA = round(adn_MDA$median_mda, digits = 2), srn_MDA = round(srn_MDA$median_mda, digits = 2), crc_MDA = round(crc_MDA$median_mda, digits = 2)) %>%
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))
